Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-04-26 ms.tex
I completed the table of all observations with some of the results in this paper.

\begin{deluxetable*}{lrrrr}
\tablecaption{List of published observations}\label{tab:obsList}
\tablewidth{0pt}
\tablehead{
\colhead{Date Start} &
\colhead{Date End} &
\colhead{Observatory} &
\colhead{Filter} &
\colhead{Reference(s)} \\
UT & UT & & & \\
 }
\startdata
2009-05-13 & 2013-05-11 & Kepler & Open CCD & \citet{borucki2010} \\
2013-07-14 & 2013-07-31 & William Herchel & $u'$, $g'$, $z'$/$i'$ & \citet{bochinski2015evolving} \\
2013-08-13 & 2013-09-03 & IRTF & $g'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
2014-08-14 & 2013-09-04 & IRTF & $g'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
\enddata
\tablenotetext{}{Summary of published observations of \sha.}
\end{deluxetable*}

@@

When using a wider aperture (9 pixels), the photometric stability is much improved and the 0.5\% transit depth is readily visible in Figure \ref{}.
The Kepler-based ephemeris indicates a transit at JD = 2457551.830.

>>>>

\begin{deluxetable*}{lrrrr}
\tablecaption{List of published observations}\label{tab:obsList}
\tablewidth{0pt}
\tablehead{
\colhead{Date Start} &
\colhead{Date End} &
\colhead{Observatory} &
\colhead{Filter} &
\colhead{Reference(s)} \\
UT & UT & & & \\
 }
\startdata
2009-05-13 & 2013-05-11 & Kepler & Open CCD & \citet{borucki2010} \\
2013-07-14 & 2013-07-31 & William Herchel & $u'$, $g'$, $z'$/$i'$ & \citet{bochinski2015evolving} \\
2013-08-13 & 2013-09-03 & IRTF & $r'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
2014-08-14 & 2013-09-04 & IRTF & $r'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
2016-06-12 & 2016-06-12 & Kuiper & Harris R & This Work \\
2016-07-12 & 2016-07-16 & Kuiper & Harris R & This Work \\
\enddata
\tablenotetext{}{Summary of published observations of \sha.}
\end{deluxetable*}

@@

When using a wider aperture (9 pixels), the photometric stability is much improved and the 0.5\% transit depth is readily visible in Figure \ref{fig:refCorrectedPhotAug12}.
The Kepler-based ephemeris indicates a transit at JD = 2457551.830.
